---
title: "Q1"
output: 
  word_document:
    reference_docx: output_test.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F,
                      message=F,
                      warning=F,
                      dpi=300)

load("C:/Users/u449921/Documents/MSc work/airbnb.RData")

library(tidyverse)
library(flextable)
```

## 1(a): Number of reviews each property receives in each city

### Output 1: Summarised statistics for reviews, Paris and Copenhagen
```{r first}


summary(copenhagen$reviews)

summary(paris$reviews)

```

### Table 1: Number of reviews per property, Paris and Copenhagen

```{r second}
copenhagen_join <- copenhagen %>% 
  mutate(`Number of reviews per property`=case_when(reviews==0~"a. 0",
                               reviews>0 & reviews<11~"b. 1 to 10",
                               reviews>10 & reviews<51~"c. 11 to 50",
                               reviews>50 & reviews<101~"d. 51 to 100",
                               reviews>100 & reviews<201~"e. 101 to 200",
                               reviews>200 & reviews<301~"f. 201 to 300",
                               reviews>300 & reviews<401~"g. 301 to 400",
                               T~"h. over 400")) %>% 
  group_by(`Number of reviews per property`) %>% 
  summarise(`Copenhagen total` = n()) %>% 
  mutate(sums = sum(`Copenhagen total`),
         `Copenhagen %` = round((`Copenhagen total`/sums)*100,1),
         `Copenhagen %` = paste0(`Copenhagen %`, "%"),
         `Number of reviews per property` = str_sub(`Number of reviews per property`, 4)) %>% 
  select(-3)


paris %>% 
  mutate(`Number of reviews per property`=case_when(reviews==0~"a. 0",
                               reviews>0 & reviews<11~"b. 1 to 10",
                               reviews>10 & reviews<51~"c. 11 to 50",
                               reviews>50 & reviews<101~"d. 51 to 100",
                               reviews>100 & reviews<201~"e. 101 to 200",
                               reviews>200 & reviews<301~"f. 201 to 300",
                               reviews>300 & reviews<401~"g. 301 to 400",
                               T~"h. over 400")) %>% 
  group_by(`Number of reviews per property`) %>% 
  summarise(`Paris total` = n()) %>% 
  mutate(sums = sum(`Paris total`),
         `Paris %` = round((`Paris total`/sums)*100,1),
         `Paris %` = paste0(`Paris %`, "%"),
         `Number of reviews per property` = str_sub(`Number of reviews per property`, 4)) %>% 
  select(-3) %>% 
  left_join(copenhagen_join) %>% 
  mutate_all(~replace_na(.,0)) %>% 
  add_row(`Number of reviews per property` = "TOTAL",
          `Paris total` = 70158,
          `Paris %` = "100%",
          `Copenhagen total` = 21301,
          `Copenhagen %` = "100%") %>% 
  flextable() %>% 
  width(j=c(1,2,4,5), 1.3) %>%
  border_outer(border = officer::fp_border()) %>% 
  vline(j=c(1,3), border = officer::fp_border()) %>% 
  bold(i=9) %>% 
  hline(i=8, border = officer::fp_border()) %>% 
  colformat_int(big.mark=",") %>% 
  align(j=1, align = 'left', part = 'all') 

```

### Figure 1: Boxplots and histograms for reviews, Paris and Copenhagen

```{r third, fig.dim = c(8,6)}
First <- copenhagen %>% 
  mutate(logreviews = log(reviews)) %>% 
  filter(reviews>0) %>%
  ggplot(aes(x=logreviews))+
  geom_histogram(bins = 13) +
  theme_bw() +
  labs(x= "",
       y="Count",
       title="Copenhagen") +
  scale_y_continuous(labels=scales::comma)

second <- copenhagen %>% 
  mutate(logreviews = log(reviews)) %>% 
  filter(reviews>0) %>%
  ggplot(aes(x=logreviews))+
  geom_boxplot()+
  theme_bw() +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  labs(title = "Copenhagen",
       x= "")

third <- paris %>% 
  mutate(logreviews = log(reviews)) %>% 
  filter(reviews>0) %>%
  ggplot(aes(x=logreviews))+
  geom_histogram(bins = 13) +
  theme_bw() +
  labs(x= "Number of reviews (log-transformed)",
       y="Count",
       title="Paris") +
  scale_y_continuous(labels=scales::comma) 

fourth <- paris %>% 
  mutate(logreviews = log(reviews)) %>% 
  filter(reviews>0) %>%
  ggplot(aes(x=logreviews))+
  geom_boxplot() +
  theme_bw() +
  theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
  labs(title = "Paris",
       x= "Number of reviews (log-transformed)")

ggpubr::ggarrange(First,second,third,fourth, ncol=2,nrow=2) %>% 
  ggpubr::annotate_figure(bottom = ggpubr::text_grob("Note: All properties with no reviews have been omitted", size=12))

```

\newpage

## 1(b): Room type in each property by city

### Figure 2: Roomtype by city, Paris and Copenhagen

```{r fourth, fig.dim = c(8,4)}

fig2_paris <- paris %>% 
  group_by(room_type) %>% 
  summarise(total = n()) %>% 
  mutate(tottt = sum(total),
         prop = round((total/tottt)*100,1),
         city = "Paris \n(n=70,158)")

fig2_copenhagen <- copenhagen %>% 
  group_by(room_type) %>% 
  summarise(total = n()) %>% 
  mutate(tottt = sum(total),
         prop = round((total/tottt)*100,1),
         city = "Copenhagen \n(n=21,301)")

rbind(fig2_paris,fig2_copenhagen) %>% 
  ggplot(aes(x=city, y=prop, fill=room_type))+
  geom_col() +
  theme_bw()+
  theme(legend.position = "bottom",
        legend.title = element_blank())+
  geom_text(aes(label = paste0(prop, "%")), position = position_stack(.5))+
  coord_flip() +
  labs(y="%",
       x="")
  

```

\newpage

## 1(c): Satisfaction by property

### Figure 3: Satisfaction by city, Paris and Copenhagen

```{r fifth, fig.dim = c(4,8)}
fig3_paris <- paris %>% 
  mutate(`Overall Satisfaction` = overall_satisfaction) %>% 
  ggplot(aes(x=`Overall Satisfaction`))+
  geom_histogram(bins=10) +
  geom_vline(xintercept = mean(paris$overall_satisfaction)) +
  geom_vline(xintercept = median(paris$overall_satisfaction), linetype = "dashed") +
  theme_bw()+
  scale_y_continuous(labels = scales::comma) +
  scale_x_continuous(breaks = seq(0,10, by=1))+
  labs(title = "Paris")

fig3_copenhagen <- copenhagen %>% 
  mutate(`Overall Satisfaction` = overall_satisfaction) %>% 
  ggplot(aes(x=`Overall Satisfaction`))+
  geom_histogram(bins=10) +
  geom_vline(xintercept = mean(copenhagen$overall_satisfaction)) +
  geom_vline(xintercept = median(copenhagen$overall_satisfaction), linetype = "dashed") +
  theme_bw()+
  scale_y_continuous(labels = scales::comma) +
  scale_x_continuous(breaks = seq(0,10, by=1))+
  labs(title = "Copenhagen")

ggpubr::ggarrange(fig3_paris, fig3_copenhagen, nrow=2) %>% 
  ggpubr::annotate_figure(bottom = ggpubr::text_grob("Note: Solid line is mean and dashed line is median", size=12))
###################################

```

## Output 1a: Satisfaction rating by number of reviews
```{r output}
paris %>% 
  group_by(reviews, overall_satisfaction) %>% 
  summarise(total = n()) %>% 
  mutate(totals = 70158,
         prop = (total/totals)*100) %>% 
  arrange(overall_satisfaction)

copenhagen %>% 
  group_by(reviews, overall_satisfaction) %>% 
  summarise(total = n()) %>% 
  mutate(totals = 21301,
         prop = (total/totals)*100) %>% 
  arrange(overall_satisfaction)

```
